Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-03-21 ProbabilisticCoherence.tex
Updated section 6

It is apparent that these three approaches use only part of the information available when producing coherent forecasts. This might result in inaccurate forecasts. For example, if the bottom level series are highly volatile or noisy, and hence challenging to forecast, then the resulting forecasts from the bottom-up approach are likely to be inaccurate.

@@

Although there is a rich and growing literature on producing coherent point forecasts of hierarchical time series, little  attention has been given to coherent probabilistic forecasts. The only relevant paper we are aware of is \citet{BenTaieb2017}, who recently proposed an algorithm to produce coherent probabilistic forecasts and applied it to UK electricity smart meter data. In their approach, a sample from the bottom level forecast distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy. Hence this method is a bottom-up approach. They propose to first use the MinT algorithm to reconcile the means of the bottom level forecast distributions, and then a copula-based approach is employed to model the dependency structure of the hierarchy. The resulting multi-dimensional distribution is used to generating empirical forecast distributions for all bottom-level series. Thus, while \citet{BenTaieb2017} provide coherent probabilistic forecasts, they do no forecast reconciliation of the distributions. In that sense, their approach is analogous to bottom-up point forecasting rather than forecast reconciliation.

After introducing our notation in Section \ref{sec:notation}, we define what is meant by probabilistic forecast reconciliation for hierarchical time series in Section \ref{sec:definitions}. First, we provide a new definition for coherency of point forecasts, and the reconciliation of a set of incoherent point forecasts, using  concepts related to vector spaces and measure theory. Based on these, we provide a rigorous definition for probabilistic forecast reconciliation, and how we can reconcile the incoherent forecast densities in practice.

Further, due to the aggregation structure of the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate. In Section \ref{sec:reconciliation}, we discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation, and in Section \ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts.

Some theoretical results on probabilistic forecast reconciliation in the Gaussian framework are given in Section \ref{sec:gaussian}, including a simulation study to show the importance of reconciliation in the probabilistic framework.

We conclude with some thoughts on extensions and limitations in Section \ref{sec:conclusions}.

@@

Our notation largely follows that introduced in \citet{Wickramasuriya2017}. Suppose $\bm{y}_t \in \mathbb{R}^n$ comprises all observations of the hierarchy at time $t$ and $\bm{b}_t \in \mathbb{R}^m$ comprises only the bottom level observations at time $t$. Then due to the aggregation nature of the hierarchy we have
\begin{equation}
  \bm{y}_t = \bm{Sb}_t,
\end{equation}
where $\bm{S}$ is an $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.

@@

Consider the hierarchy given in Figure \ref{fig1}.

\begin{figure}[H]
  \begin{center}
    \leaf{AA} \leaf{AB} 
    \branch{2}{A}
    \leaf{BA} \leaf{BB}
    \branch{2}{B}
    \branch{2}{Tot}
    \qobitree
  \end{center}
  \caption{Two level hierarchical diagram}\label{fig1}
\end{figure}

@@

We illustrate Definition \ref{def:cohprob} in Figure \ref{fig2}, showing $\bm{S}$ mapping any set $\bm{A}\in\mathbb{R}^m$ to the coherent space.

@@

    \end{tikzpicture}
    \newline
  \end{center}
  \caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to $\mathbb{C}^m$ through the mapping $\bm{S}$}\label{fig2}
\end{figure}

Definition \ref{def:cohprob} implies the probability measure on $\mathbb{C}^m$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$. Hence, there is no density anywhere outside the linear subspace $\mathbb{C}^m$. That is, a \textit{coherent probability density forecast} is any density $\bm{f}(\breve{\bm{y}}_{t+h})$ such that $\bm{f}(\breve{\bm{y}}_{t+h})=0$ for all $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}^{n-m}$.

@@

Consider a simple hierarchy with two bottom level series $A$ and $B$ that add up to the top level series $Tot$. Suppose the forecasts of these series at time $t+h$ are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$. Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$. This implies that, even though  $\breve{\bm{y}}_{t+h} \in \mathbb{R}^3$, the points actually lie in $\mathbb{C}^2$, which is a two dimensional subspace within that $\mathbb{R}^3$ space. Therefore, any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$ is impossible, so that $f(\breve{\bm{y}}_{t+h})=0$ for any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$.

For a particular coherent subspace $\mathbb{C}^m$, there exist several distinct basis vectors. For example, in the small hierarchy considered above, 
 $\{(1 ~1 ~0)', (1 ~0 ~1)'\}$, 
 $\{(1 ~ 0 ~ 1)',(0~1~-\!\!1)'\}$ 
and the singular value decomposition of these two are some alternative basis vectors that span the same $\mathbb{C}^m$. Given a basis for $\mathbb{C}^m$, every series of the hierarchy can be linearly determined as a linear combination of those basis vectors. We refer to the coefficients of these linear combinations as the \textit{basis series}. It is apparent that these basis series are $m$-dimensional and linearly independent in a given hierarchy. For example, in the smallest hierarchy, $(A,B)$ and $(Tot,A)$ are the basis series corresponding to the basis vectors 
 $\{(1 ~1 ~0)', (1 ~0 ~1)'\}$, 
 $\{(1 ~ 0 ~ 1)',(0~1~-\!\!1)'\}$
respectively. Thus it is clear that the set of bottom level series is a basis series that corresponds to the column vectors of $\bm{S}$.

Because the basis is not unique for a given coherent subspace, Definition \ref{def:cohprob} is not unique, and one can redefine the coherent probabilistic forecasts with respect to any basis. However, we stick to Definition \ref{def:cohprob} and consider the basis defined by the columns of $\bm{S}$ in what follows.

Definitions \ref{def:cohpoint} and \ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section. In contrast to our definition, \citet{BenTaieb2017} define coherent probabilistic forecasts in terms of convolutions. According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.  While this is consistent with our definition, it is not easy to extend their definition to deal with probabilistic reconciliation.

@@

Definition \ref{def:reconpoint} allows for both linear and non-linear reconciliation. In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear, while if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(\cdot)$ will linearly project incoherent point forecasts onto $\mathbb{C}^m$. Previous studies in hierarchical point forecasting have only focussed on the linear case, $\bm{g}(\bm{y}) = \bm{P}\bm{y}$, where $\bm{P}$ is an $m \times n$ matrix, and so $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.

Using Definition \ref{def:reconpoint}, we can now explain previous results for linear forecast reconciliation. Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ comprise the columns that span $\bm{\mathbb{N}}^{n-m}$, which is orthogonal to $\mathbb{C}^m$. Note that $\bm{R}$ is not unique; one example is a matrix whose columns represent the aggregation constraints for a given hierarchy. For the hierarchy in example 1, 
$$ 
\bm{S} = 
\begin{pmatrix} 
1& 1 \\ 1 & 0 \\ 0&1 
\end{pmatrix} 
\quad \text{and} \quad 
\bm{R} = 
\begin{pmatrix}  
1 \\ -1 \\ -1 
\end{pmatrix}.
$$

Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$. Now, using the insights of Definition \ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.

\subsubsection*{Step 1: Obtaining reconciled bottom level point forecasts}

For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$. Let $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$ denote these coordinates. Note that $\tilde{\bm{b}}_{t+h}$ is a basis series which is equivalent to the reconciled bottom level series, and which corresponds to the linear combination coefficients of the basis $\{\bm{s}_1,\dots,\bm{s}_m\}$. Similarly, $\tilde{\bm{t}}_{t+h}$ is another basis series corresponding to the linear combination coefficients of the basis $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$. Then from basic properties of linear algebra it follows that, 
\[
(\bm{S} ~ \vdots~ \bm{R})
(\tilde{\bm{b}}'_{t+h},~ \tilde{\bm{t}}'_{t+h})'
= \hat{\bm{y}}_{t+h},
\]
\[
\hat{\bm{y}}_{t+h} = \bm{S}\tilde{\bm{b}}_{t+h} +  \bm{R}\tilde{\bm{t}}_{t+h},
\]
and
\begin{equation}\label{4.3}
(\tilde{\bm{b}}'_{t+h}, ~ \tilde{\bm{t}}'_{t+h})' =
(\bm{S} ~ \vdots~ \bm{R})^{-1}
\hat{\bm{y}}_{t+h}.
\end{equation}

In order to find $(\bm{S} ~ \vdots~ \bm{R})^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
respectively. Then $(\bm{S} ~ \vdots~ \bm{R})^{-1}$ is given by,
\begin{equation}
(\bm{S} ~ \vdots~ \bm{R})^{-1} = \begin{pmatrix}
(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
\end{pmatrix}.
\end{equation}
Thus we have,
\begin{equation} \label{4.4}
\begin{pmatrix}
\tilde{\bm{b}}_{t+h} \\ \cdots \\ \tilde{\bm{t}}_{t+h}
\end{pmatrix} = \begin{pmatrix}
(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
\end{pmatrix}\hat{\bm{y}}_{t+h}.
\end{equation}

From \eqref{4.4} it follows that,
\begin{equation}
\tilde{\bm{b}}_{t+h}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}
\end{equation}

@@

\citet{Hyndman2011} proposed to choose
\begin{equation*}
\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
\end{equation*}
where, in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by,
\begin{equation}
\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}.
\end{equation}
They referred this to as the OLS solution and the loss function they considered is equivalent to the Euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$; i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.

According to a recent study by \citet{Wickramasuriya2017}, selecting $\bm{R}'_\bot = \bm{S}'\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecast errors under the property of unbiasedness, where $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors. This will result in
\begin{equation*}
\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}'\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
\end{equation*}
and thus,
\begin{equation}
\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}' \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
\end{equation}

@@

Let the density of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ be denoted by $\bm{f_B}(\cdot)$. Then it follows from  \eqref{4.3}, and standard results for densities of transformed variables, that
\begin{equation}\label{4.5}
\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \,\Big|\bm{S} ~ \vdots~ \bm{R}\Big|,
\end{equation}
where $|\cdot|$ denotes the determinant of a matrix. Now that we have the density of $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating \eqref{4.5} over the range of $\tilde{\bm{t}}_{t+h}$. This will result in the reconciled density of the bottom level series $\tilde{\bm{b}}_{t+h}$,
\begin{equation}\label{4.6}
\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{\lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h})\,  \Big|\bm{S} ~ \vdots~ \bm{R}\Big| \, d\tilde{\bm{t}}_{t+h}.
\end{equation}

Finally to get the reconciled density of the whole hierarchy, we simply follow Definition \ref{def:cohprob} to obtain
\begin{equation}\label{4.7}
\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\bm{S}\circ \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h}).
\end{equation}
This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the space $\mathbb{C}^m<\mathbb{R}^n$. The following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.

@@

Suppose $\mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \overset{d}{\leftrightarrow} \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$. Then from \eqref{4.5} it follows that
\begin{equation*}

@@

\end{equation*}

@@

Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$. Then from \eqref{4.7} it follows that
\begin{equation}
\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
\end{equation}
Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is\\
$\mathscr{N}(\bm{SP}\bm{\hat{\mu}}_{t+h},~ \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}')$.

@@

Table \ref{table:scoringrules} summarizes a few existing proper scoring rules.

>>>>

It is apparent that these three approaches use only part of the information available when producing coherent forecasts. This might result in inaccurate forecasts. For example, if the bottom-level series are highly volatile or noisy, and hence challenging to forecast, then the resulting forecasts from the bottom-up approach are likely to be inaccurate.

@@

Although there is a rich and growing literature on producing coherent point forecasts of hierarchical time series, little  attention has been given to coherent probabilistic forecasts. The only relevant paper we are aware of is \citet{BenTaieb2017}, who recently proposed an algorithm to produce coherent probabilistic forecasts and applied it to UK electricity smart meter data. In their approach, a sample from the bottom-level forecast distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy. Hence this method is a bottom-up approach. They propose to first use the MinT algorithm to reconcile the means of the bottom-level forecast distributions, and then a copula-based approach is employed to model the dependency structure of the hierarchy. The resulting multi-dimensional distribution is used to generating empirical forecast distributions for all bottom-level series. Thus, while \citet{BenTaieb2017} provide coherent probabilistic forecasts, they do no forecast reconciliation of the distributions. In that sense, their approach is analogous to bottom-up point forecasting rather than forecast reconciliation.

After introducing our notation in Section~\ref{sec:notation}, we define what is meant by probabilistic forecast reconciliation for hierarchical time series in Section~\ref{sec:definitions}. First, we provide a new definition for coherency of point forecasts, and the reconciliation of a set of incoherent point forecasts, using  concepts related to vector spaces and measure theory. Based on these, we provide a rigorous definition for probabilistic forecast reconciliation, and how we can reconcile the incoherent forecast densities in practice.

Further, due to the aggregation structure of the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate. In Section~\ref{sec:reconciliation}, we discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation, and in Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts.

Some theoretical results on probabilistic forecast reconciliation in the Gaussian framework are given in Section~\ref{sec:gaussian}, including a simulation study to show the importance of reconciliation in the probabilistic framework.

We conclude with some thoughts on extensions and limitations in Section~\ref{sec:conclusions}.

@@

Our notation largely follows that introduced in \citet{Wickramasuriya2017}. Suppose $\bm{y}_t \in \mathbb{R}^n$ comprises all observations of the hierarchy at time $t$ and $\bm{b}_t \in \mathbb{R}^m$ comprises only the bottom-level observations at time $t$. Then due to the aggregation nature of the hierarchy we have
\begin{equation}
  \bm{y}_t = \bm{Sb}_t,
\end{equation}
where $\bm{S}$ is an $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.

@@

Consider the hierarchy given in Figure~\ref{fig1}.

\begin{figure}[H]
  \begin{center}
    \leaf{AA} \leaf{AB} 
    \branch{2}{A}
    \leaf{BA} \leaf{BB}
    \branch{2}{B}
    \branch{2}{Tot}
    \qobitree
  \end{center}
  \caption{Two level hierarchical diagram.}\label{fig1}
\end{figure}

@@

We illustrate Definition~\ref{def:cohprob} in Figure~\ref{fig2}, showing $\bm{S}$ mapping any set $\bm{A}\in\mathbb{R}^m$ to the coherent space.

@@

    \end{tikzpicture}
    \newline
  \end{center}
  \caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to $\mathbb{C}^m$ through the mapping $\bm{S}$.}\label{fig2}
\end{figure}

Definition~\ref{def:cohprob} implies the probability measure on $\mathbb{C}^m$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$. Hence, there is no density anywhere outside the linear subspace $\mathbb{C}^m$. That is, a \textit{coherent probability density forecast} is any density $\bm{f}(\breve{\bm{y}}_{t+h})$ such that $\bm{f}(\breve{\bm{y}}_{t+h})=0$ for all $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}^{n-m}$.

@@

Consider a simple hierarchy with two bottom-level series $A$ and $B$ that add up to the top level series $Tot$. Suppose the forecasts of these series at time $t+h$ are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$. Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$. This implies that, even though  $\breve{\bm{y}}_{t+h} \in \mathbb{R}^3$, the points actually lie in $\mathbb{C}^2$, which is a two dimensional subspace within that $\mathbb{R}^3$ space. Therefore, any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$ is impossible, so that $f(\breve{\bm{y}}_{t+h})=0$ for any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$.

For a particular coherent subspace $\mathbb{C}^m$, there exist several distinct basis vectors. For example, in the small hierarchy considered above, 
 $\{(1 ~1 ~0)', (1 ~0 ~1)'\}$, 
 $\{(1 ~ 0 ~ 1)',(0~1~-\!\!1)'\}$ 
and the singular value decomposition of these two are some alternative basis vectors that span the same $\mathbb{C}^m$. Given a basis for $\mathbb{C}^m$, every series of the hierarchy can be linearly determined as a linear combination of those basis vectors. We refer to the coefficients of these linear combinations as the \textit{basis series}. It is apparent that these basis series are $m$-dimensional and linearly independent in a given hierarchy. For example, in the smallest hierarchy, $(A,B)$ and $(Tot,A)$ are the basis series corresponding to the basis vectors 
 $\{(1 ~1 ~0)', (1 ~0 ~1)'\}$, 
 $\{(1 ~ 0 ~ 1)',(0~1~-\!\!1)'\}$
respectively. Thus it is clear that the set of bottom-level series is a basis series that corresponds to the column vectors of $\bm{S}$.

Because the basis is not unique for a given coherent subspace, Definition~\ref{def:cohprob} is not unique, and one can redefine the coherent probabilistic forecasts with respect to any basis. However, we stick to Definition~\ref{def:cohprob} and consider the basis defined by the columns of $\bm{S}$ in what follows.

Definitions~\ref{def:cohpoint} and~\ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section. In contrast to our definition, \citet{BenTaieb2017} define coherent probabilistic forecasts in terms of convolutions. According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.  While this is consistent with our definition, it is not easy to extend their definition to deal with probabilistic reconciliation.

@@

Definition~\ref{def:reconpoint} allows for both linear and non-linear reconciliation. In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear, while if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(\cdot)$ will linearly project incoherent point forecasts onto $\mathbb{C}^m$. Previous studies in hierarchical point forecasting have only focussed on the linear case, $\bm{g}(\bm{y}) = \bm{P}\bm{y}$, where $\bm{P}$ is an $m \times n$ matrix, and so $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.

Using Definition~\ref{def:reconpoint}, we can now explain previous results for linear forecast reconciliation. Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ comprise the columns that span $\bm{\mathbb{N}}^{n-m}$, which is orthogonal to $\mathbb{C}^m$. Note that $\bm{R}$ is not unique; one example is a matrix whose columns represent the aggregation constraints for a given hierarchy. For the hierarchy in example 1, 
$$ 
\bm{S} = 
\begin{pmatrix} 
1& 1 \\ 1 & 0 \\ 0&1 
\end{pmatrix} 
\quad \text{and} \quad 
\bm{R} = 
\begin{pmatrix}  
1 \\ -1 \\ -1 
\end{pmatrix}.
$$

Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$. Now, using the insights of Definition~\ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.

\subsubsection*{Step 1: Obtaining reconciled bottom-level point forecasts}

For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$. Let $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$ denote these coordinates. Note that $\tilde{\bm{b}}_{t+h}$ is a basis series which is equivalent to the reconciled bottom-level series, and which corresponds to the linear combination coefficients of the basis $\{\bm{s}_1,\dots,\bm{s}_m\}$. Similarly, $\tilde{\bm{t}}_{t+h}$ is another basis series corresponding to the linear combination coefficients of the basis $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$. Then from basic properties of linear algebra it follows that 
\[
(\bm{S} ~ \vdots~ \bm{R})
(\tilde{\bm{b}}'_{t+h},~ \tilde{\bm{t}}'_{t+h})'
= \hat{\bm{y}}_{t+h},
\]
\[
\hat{\bm{y}}_{t+h} = \bm{S}\tilde{\bm{b}}_{t+h} +  \bm{R}\tilde{\bm{t}}_{t+h},
\]
and
\begin{equation}\label{4.3}
(\tilde{\bm{b}}'_{t+h}, ~ \tilde{\bm{t}}'_{t+h})' =
(\bm{S} ~ \vdots~ \bm{R})^{-1}
\hat{\bm{y}}_{t+h}.
\end{equation}

In order to find $(\bm{S} ~ \vdots~ \bm{R})^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
respectively. Then $(\bm{S} ~ \vdots~ \bm{R})^{-1}$ is given by
\begin{equation}
(\bm{S} ~ \vdots~ \bm{R})^{-1} = \begin{pmatrix}
(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
\end{pmatrix}.
\end{equation}
Thus we have,
\begin{equation} \label{4.4}
\begin{pmatrix}
\tilde{\bm{b}}_{t+h} \\ \cdots \\ \tilde{\bm{t}}_{t+h}
\end{pmatrix} = \begin{pmatrix}
(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
\end{pmatrix}\hat{\bm{y}}_{t+h}.
\end{equation}

From \eqref{4.4} it follows that
\begin{equation}
\tilde{\bm{b}}_{t+h}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}
\end{equation}

@@

\citet{Hyndman2011} proposed to choose
\begin{equation}
\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
\end{equation}
where, in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by
\begin{equation}
\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}.
\end{equation}
They referred this to as the OLS solution and the loss function they considered is equivalent to the Euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$; i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.

According to a recent study by \citet{Wickramasuriya2017}, selecting $\bm{R}'_\bot = \bm{S}'\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecast errors under the property of unbiasedness, where $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors. This will result in
\begin{equation}
\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}'\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
\end{equation}
and thus,
\begin{equation}
\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}' \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
\end{equation}

@@

Let the density of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ be denoted by $\bm{f_B}(\cdot)$. Then it follows from  \eqref{4.3}, and standard results for densities of transformed variables, that
\begin{equation}\label{4.5}
\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \,\Big|\bm{S} ~ \vdots~ \bm{R}\Big|,
\end{equation}
where $|\cdot|$ denotes the determinant of a matrix. Now that we have the density of $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating \eqref{4.5} over the range of $\tilde{\bm{t}}_{t+h}$. This will result in the reconciled density of the bottom-level series $\tilde{\bm{b}}_{t+h}$,
\begin{equation}\label{4.6}
\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{\lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h})\,  \Big|\bm{S} ~ \vdots~ \bm{R}\Big| \, d\tilde{\bm{t}}_{t+h}.
\end{equation}

Finally to get the reconciled density of the whole hierarchy, we simply follow Definition~\ref{def:cohprob} to obtain
\begin{equation}\label{4.7}
\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\bm{S}\circ \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h}).
\end{equation}
This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the space $\mathbb{C}^m<\mathbb{R}^n$. The following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.

@@

Suppose $\mathcal{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \overset{d}{\leftrightarrow} \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$. Then from \eqref{4.5} it follows that
\begin{equation}

@@

@@

Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$. Then from \eqref{4.7} it follows that
\begin{equation}\label{eq:gaussianreconciled}
\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
\end{equation}
Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is\\
$\mathcal{N}(\bm{SP}\bm{\hat{\mu}}_{t+h},~ \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}')$.

@@

Table~\ref{table:scoringrules} summarizes a few existing proper scoring rules.
